---
name: Thiago 
surname: Scot
#position: "Economist"
address: "Development Impact Evaluation (DIME), World Bank"
www: www.thiagoscot.com
email: "tscot@worldbank.org"
#orcid: 0000-0001-6087-0428
#researchgate: Han_Zhang175
#github: thiagoscot
#twitter: \_HanZhang_
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=lua/strong.lua"] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
#rmarkdown::pandoc_version()
```
# Current Appointment

```{r}
tribble(
  ~Appointment,
  ~Year,
  "Economist at World Bank Research Group, Development Impact Evaluation Department",
  "2021 - "
) %>%
  detailed_entries(
    what = Appointment,
    when = Year
  )
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution,
  "PhD, Haas School of Business",
  "2016 - 2021",
  "University of California, Berkeley",
  "M.A., Economics",
  "2011 - 2013",
  "Pontifícia Universidade Católica (PUC-Rio) - Brazil",
  "B.A., International Relations",
  "2005 - 2009",
  "Pontifícia Universidade Católica (PUC-Rio) - Brazil"
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution
  )
```

# Peer Reviewed Publications 

*Corporate Taxation and Evasion Responses: Evidence from a Minimum Tax in Honduras* (with Felipe Lobel and Pedro Zuniga) - **Conditionally Accepted at American Economic Journal: Economic Policy**

*Selecting Top Bureaucrats: Admission Exams and Performance in Brazil* (with [Laura Schiavon](https://www.lauraschiavon.com/) and [Ricardo Dahis](https://www.ricardodahis.com/)) - **Accepted at Review of Economics and Statistics**

*Political Selection and Bureaucratic Productivity* (with [James Habyarimana](https://gufaculty360.georgetown.edu/s/contact/00336000014RXPpAAO/james-habyarimana) and [Stuti Khemani](https://sites.google.com/view/stutikhemani/)). **Accepted at Economica**

# Working papers and work in progress

*Targeting in Tax Compliance Interventions: Experimental Evidence from Honduras* (with Giselle Del Carmen and Edgardo Enrique Hernandez)

*Estimates of Top Income Inequality using Administrative Data in Honduras* (with Santiago Garriga and Edgardo Enrique Hernandez)

*Building State Capacity: What is the Impact of Development Projects?* (with [Vincenzo di Maro](https://sites.google.com/site/vincenzodimaro/), [David Evans](https://sites.google.com/site/davidkevans/) and
[Stuti Khemani](https://sites.google.com/view/stutikhemani/))

# Conferences and Invited Talks

```{r}
tribble(
  ~ Events, ~ Year, 
  'International Institute of Public Finance (IIPF), Zurich Public Finance in Developing Countries (discussant)',
  '2022',
  'World Bank DIME, Tulane University, Center for Global Development, PUC-Rio, Insper, NBER Public
Economics Spring Meeting [Job Market year]', 
'2021',
'International Institute of Public Finance (IIPF); Society for Institutional and Organizational Economics(SIOE); Berkeley Public Finance Seminar; Berkeley Development Seminar; NTA 113th Annual Conference; EGSC at Washington University', 
'2020',
'NOVAFRICA Conference on Economic Development in Africa',
'2019',
'World Bank ABCDE Conference',
'2018') %>% 
  detailed_entries(
    what = Events,
    when = Year
  )
```

# Awards and Grants

```{r}
tribble(
  ~Grant, ~Year,
  'Knowledge for Change Program (KCP) *Understanding the determinants of public procurement efficiency: evidence from administrative and survey data from Brazil*',
  '2022',
  'Global Tax Program *EFT Strategies to Improve Tax Compliance*', 
  '2022',
  'Global Tax Program *Tax Policy Analysis to build capacity and improve equity*', 
  '2022',
  'International Tax and Public Finance PhD Student award at IIPF',
  '2020',
  'UC Berkeley’s 2019 Outstanding GSI Award (awarded to top 10% of TAs)',
  '2019',
'Weiss Family Fund Exploratory Grant',
'2017',
 'Winner of ANBIMA Capital Markets Award for best Master’s thesis project in Brazil',
 '2012') %>% 
  detailed_entries(
    what = Grant,
    when = Year
  ) 
```

# Professional Service

**Refereeing**: Journal of the European Economic Association, Journal of Public Economics, World Bank Economic Review, International Tax and Public Finance (ITAX).  

# Professional Experience

```{r}
tribble(
  ~ Institution, ~ Year, ~ Position,
  "The World Bank, Washington, DC",
  "2014 - 2016",
  "Consultant at Poverty and Inequality Global Practice (Latin America)",
  "Opus Asset Management",
  "2013",
  "International Economist"
) %>%
  detailed_entries(
    what = Position,
    with = Institution,
    when = Year
  )
```

# Languages

Portuguese (native); English (fluent); French (fluent); Spanish (fluent)