---
name: Thiago 
surname: Scot
#position: "Economist"
address: "Development Impact Department (DECDI), World Bank"
www: www.thiagoscot.com
email: "tscot@worldbank.org"
#orcid: 0000-0001-6087-0428
#researchgate: Han_Zhang175
#github: thiagoscot
#twitter: \_HanZhang_
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=lua/strong.lua"] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
#rmarkdown::pandoc_version()
```
# Current Appointment

```{r}
tribble(
  ~Appointment,
  ~Year,
  "Economist at World Bank, Development Impact Department (DECDI)",
  "2021 - "
) %>%
  detailed_entries(
    what = Appointment,
    when = Year
  )
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution,
  "PhD, Haas School of Business",
  "2016 - 2021",
  "University of California, Berkeley",
  "M.A., Economics",
  "2011 - 2013",
  "Pontifícia Universidade Católica (PUC-Rio) - Brazil",
  "B.A., International Relations",
  "2005 - 2009",
  "Pontifícia Universidade Católica (PUC-Rio) - Brazil"
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution
  )
```

# Peer Reviewed Publications 

Two Decades of Top Income Shares in Honduras &nbsp; (with Giselle Del Carmen, Santiago Garriga and Wilman Nuñez) **Journal of Public Economics 2025, Volume 246**

Corporate Taxation and Evasion Responses: Evidence from a Minimum Tax in Honduras &nbsp;  (with Felipe Lobel and Pedro Zuniga) - **American Economic Journal: Economic Policy, 16 (1): 482–517 2024. DOI: 10.1257/pol.20210587**

Selecting Top Bureaucrats: Admission Exams and Performance in Brazil &nbsp; (with [Laura Schiavon](https://www.lauraschiavon.com/) and [Ricardo Dahis](https://www.ricardodahis.com/)) - **The Review of Economics and Statistics 2023; doi: https://doi.org/10.1162/rest_a_01311 **

Political Selection and Bureaucratic Productivity &nbsp; (with [James Habyarimana](https://gufaculty360.georgetown.edu/s/contact/00336000014RXPpAAO/james-habyarimana) and [Stuti Khemani](https://sites.google.com/view/stutikhemani/)). **Economica. 2023; 90(359):  746 - 779. doi: 10.1111/ecca.12470**

# Working papers and work in progress

Tax Progressivity and Inequality in Brazil: Evidence from Integrated Administrative Data &nbsp;(with Theo Palomo, Davi Bhering, Pierre Bachas, Luciana Barcarolo, Celso Campos, Javier Feinmann, Leonardo Moreira, Gabriel Zucman) *EUTO Working Paper n9 2025*

MiDES: New Data and Facts from Local Procurement and Budget Execution in Brazil.  &nbsp; (with [Ricardo Dahis](https://www.ricardodahis.com/), Lucas Nascimento, [Bernardo Ricca](https://bernardoricca.wixsite.com/bricca) and Nathalia Sales) *Policy Research working paper ; no. WPS 10598; RRR Washington, D.C. : World Bank Group.*

VAT Refunds and Firms’ Performance: Evidence from a Withholding Reform in Honduras &nbsp; (with David Pinto and Jose Carlo Bermudez) *Policy Research working paper ; no. WPS 10996; RRR Washington, D.C. : World Bank Group.*

Speed of Payment in Procurement Contracts: The Role of Political Connections &nbsp; (with [Ricardo Dahis](https://www.ricardodahis.com/) and [Bernardo Ricca](https://bernardoricca.wixsite.com/bricca)) *Available at SSRN: https://ssrn.com/abstract=3934021*


Corporate Responses to Size-Based Tax Rates in Lithuania &nbsp; (with [Pablo Garriga](https://pablogarriga.github.io/)) *World Bank Policy Research working paper n. WPS 10500*

Targeting in Tax Compliance Interventions: Experimental Evidence from Honduras &nbsp; (with Giselle Del Carmen and Edgardo Enrique Hernandez) *World Bank Policy Research working paper n. WPS 9967*

Building State Capacity: What is the Impact of Development Projects? &nbsp; (with [Vincenzo di Maro](https://sites.google.com/site/vincenzodimaro/), [David Evans](https://sites.google.com/site/davidkevans/) and
[Stuti Khemani](https://sites.google.com/view/stutikhemani/)) *World Bank Policy Research working paper n. WPS 9875*

The Financial Risk of Winning a Procurement Contract: Evidence from Chile &nbsp; (with [Andres Gonzalez-Lira](https://sites.google.com/view/andres-gonzalez-lira))



# Conferences and Invited Talks

```{r}
tribble(
  ~ Events, ~ Year,
  'NBER Public Economics Fall meeting, IMF Fiscal Affairs Department (FAD), IFS TaxDev seminar, Zurich Conference on Public Finance in Developing Countries',
  '2024',
  'Commitment to Equity (CEQ) & World Bank workshop',
  '2023',
  'International Institute of Public Finance (IIPF), Zurich Conference on Public Finance in Developing Countries (discussant)',
  '2022',
  'World Bank DIME, Tulane University, Center for Global Development, PUC-Rio, Insper, NBER Public
Economics Spring Meeting [Job Market year]', 
'2021',
'International Institute of Public Finance (IIPF); Society for Institutional and Organizational Economics(SIOE); Berkeley Public Finance Seminar; Berkeley Development Seminar; NTA 113th Annual Conference; EGSC at Washington University', 
'2020',
'NOVAFRICA Conference on Economic Development in Africa',
'2019',
'World Bank ABCDE Conference',
'2018') %>% 
  detailed_entries(
    what = Events,
    when = Year
  )
```

# Awards and Grants

```{r}
tribble(
  ~Grant, ~Year,
  'Research Support Budget (RSB) - Public procurement and private sector: evidence from a novel dataset on subnational procurement in Brazil ',
  '2022',
  'Knowledge for Change Program (KCP) - Understanding the determinants of public procurement efficiency: evidence from administrative and survey data from Brazil',
  '2022',
  'Global Tax Program -- EFT -  Strategies to Improve Tax Compliance', 
  '2022',
  'Global Tax Program -- Tax Policy Analysis to build capacity and improve equity', 
  '2022',
  'International Tax and Public Finance PhD Student award at IIPF',
  '2020',
  'UC Berkeley’s 2019 Outstanding GSI Award (awarded to top 10% of TAs)',
  '2019',
'Weiss Family Fund Exploratory Grant',
'2017',
 'Winner of ANBIMA Capital Markets Award for best Master’s thesis project in Brazil',
 '2012') %>% 
  detailed_entries(
    what = Grant,
    when = Year
  ) 
```

# Professional Service

**Refereeing**: American Economic Journal: Economic Policy, Journal of the European Economic Association, Journal of Public Economics, World Bank Economic Review, International Tax and Public Finance (ITAX), Economic Development and Cultural Change.  

**Conference organization**: World Bank/IFS/ODI Tax Conference (2022; 2023)

# Professional Experience

```{r}
tribble(
  ~ Institution, ~ Year, ~ Position,
  "The World Bank, Washington, DC",
  "2014 - 2016",
  "Consultant at Poverty and Inequality Global Practice (Latin America)",
  "Opus Asset Management",
  "2013",
  "International Economist"
) %>%
  detailed_entries(
    what = Position,
    with = Institution,
    when = Year
  )
```

# Languages

Portuguese (native); English (fluent); French (fluent); Spanish (fluent)

# Pre-doctoral policy research

*Strengthening Public Health Systems: Policy Ideas from a Governance Perspective* (with Stuti Khemani and Sarang Chaudhary). World Bank Policy Research Working Paper No. 9220, 2020.

*Investing in people to fight poverty in Haiti: reflections for evidence-based policy making (Haiti Poverty Assessment)* (with Federica Marzo, Pablo Facundo Cuevas and Natalia Garbiras). December 2014

*But what is the poverty rate today? Testing poverty nowcasting methods in Latin America and the Caribbean* (with
German Caruso, Leonardo Lucchetti, Eduardo Malasquez and Andres Castaneda). World Bank Policy Research
Working Paper No. 8104.

*Sifting through the Data: Labor Markets in Haiti through a Turbulent Decade (2001-2012)* (with Aude- Sophie Rodella and P. Facundo Cuevas). World Bank Policy Research Working Paper No. 7562

*Cyclical Variations in Participation and Employment in Urban Brazil* (with Emmanuel Skoufias and Renata Gukovas).
No 24952, World Bank Other Operational Studies, May 2016.